### 2014-12-27 paper_10_intro.tex
added software dev analytics
updates to intro

One example of scoring software development is presented by Jones \cite{Jones2012}. The methodology looks
for the presence of various techniques used in software engineering.  The methodology provides a score based upon the 
productivity and quality increase of the technique being evaluated.  A couple example techniques are: 
automated source code analysis and continuous integration.  The end result is a score in range $[-10,10]$. 
While the single number score is nice, it does not account for the entirety of the software development lifecycle.

@@

\subsubsection{SOFTWARE ANALYTICS}
See also \cite{Buse2010}.

@@

>>>>

One example of scoring software development is presented by Jones \cite{Jones2012}. The methodology looks
for the presence of various techniques used in software engineering.  The methodology provides a score based upon the 
productivity and quality increase of the technique being evaluated.  Points are positive or negative based upon the 
presense of various techniques. A couple example techniques are: 
automated source code analysis and continuous integration.  The end result is a score in range $[-10,10]$. 
While the result is a single number score, it does not account for the entirety of the software development lifecycle.

@@

\subsubsection{SOFTWARE ANALYTICS}
See also \cite{Buse2010}.  There is a subsection named
software development analytics \cite{Menzies2012}.

@@

    So it has been shown, there exist many attempts to 
    evaluate portions of the a software development 
    organization.  None of the the attempts provide
    a single number score for the entirety of the 
    organization.  Most of the techniques focus on
    specific portions of the software development 
    lifecycle, namely the development portion.
